%-------------------------
% Resume in Latex
% Author : Ryan Tran
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-3pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Ryan Tran} \\ \vspace{1pt}
    \small 678-670-9868 $|$ \href{mailto:concepting@protonmail.com}{\underline{concepting@protonmail.com}} $|$ 
    \href{https://linkedin.com/in/RyanTren/}{\underline{linkedin.com/in/RyanTren/}} $|$
    \href{https://github.com/RyanTren}{\underline{github.com/RyanTren}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Kennesaw State University}{Marietta, GA}
      {Bachelor of Science in Computer Science}{Expected Graduation: May 2026}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineering Intern}{Sep. 2024 -- Present}
      {Aayats}{Atlanta, GA}
      \resumeItemListStart
        \resumeItem{Developed an AI-metadata generation system for 1,000+ music producer\texttt{'}s beats using machine learning models, open-source libraries, and APIs, streamlining content categorization.
        }
        \resumeItem{Fine-tuned advanced LLMs (e.g., Llama 3.2, Mistral, Phi \& Gemma) on Tesla T4 GPUs, achieving a 2-5x performance boost with 80\% reduced memory usage.}
        \resumeItem{Enhanced app stability by reducing reported issues by 25\% through identifying and resolving critical bugs, performing comprehensive testing, and conducting code reviews for Flutter/Dart iOS Application.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Undergraduate Artificial Intelligence Research}{July 2024 -- December 2024}
      {Kennesaw State University}{Marietta, GA}
      \resumeItemListStart
        \resumeItem{Analyzed multi-modal data to identify key characteristics, enhancing understanding of emotional well-being.}
        \resumeItem{Contributed to developing machine learning, deep learning, and natural language processing algorithms, improving the AI system's performance.}
        \resumeItem{Co-authored and presented research findings at internal and external venues, including conferences and workshops, promoting advancements in emotional AI.}
      \resumeItemListEnd

      \resumeSubheading
      {Software Engineering Fellow}{July 2024 -- September 2024}
      {Headstarter AI}{Long Island City, NY}
      \resumeItemListStart
        \resumeItem{Engineered and deployed 5+ AI-powered web applications using React JS, Next.js, Firebase, and Vercel, scaling to 200+ users each through agile development practices.}
        \resumeItem{Integrated CI/CD pipelines to enable seamless and iterative deployments, reducing deployment errors and increasing developer productivity.}
        \resumeItem{Scaled each web-app to 200+ users, iterated on user feedback to make continuous optimizations}
        \resumeItem{Mentored by Amazon, Bloomberg, and Capital One engineers on Agile, CI/CD, Git, and micro-service patterns}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI Mental Health SaaS} $|$ \emph{Next.js, JavaScript, OpenAI, Clerk/Stripe, Firebase}}{August 2024 -- September 2024}
          \resumeItemListStart
            \resumeItem{Achieved the successful launch of an AI-powered mental health SaaS application, by developing the platform with Next.js, Firebase, and OpenAI, which enabled users to create AI-generated solutions.}
            \resumeItem{Implemented Stripe for payment processing and Clerk for authentication, resulting in a secure and scalable user experience.}
            \resumeItem{Secured over 100 users and 10 paid customers within the first month, by launching the application and tracked user engagement through built-in analytics.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Automated Restaurant POS Application} $|$ \emph{Java, Docker, MySQL, GIT}}{January 2024 -- May 2024}
          \resumeItemListStart
            \resumeItem{Created a POS system using Java/JavaFX for GUI and Docker/MySQL for the database, improving operational efficiency by 35\%.}
            \resumeItem{Delivered real-time insights to management through automated data collection and analysis, boosting revenue optimization by 25\% and improving functional efficiency by 30\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C\#, C++, JavaScript, TypeScript, R, Swift, HTML/CSS, SQL, MySQL} \\
     \textbf{Frameworks}{: React, Next.js, Node.js, Material-UI, Aceternity, Shadcn, FastAPI} \\
     \textbf{Developer Tools}{: Git, Docker, AWS, Google Cloud Platform, Postman, VSCode/Visual Studio, XCode, IntelliJ} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
